Technical Report

### 2018-07-02 fully-abstract-comp/technical-report.tex
Fix a problem related to steps accounting in the component-related lemmas.

\begin{align*}
  \lrcomp(W) &=
  \left\{\begin{aligned}
     &\npair{\var{comp},\var{comp}} \;\mid \;\\
      &\qquad\var{comp} = (\mscode,\msdata,\overline{a_{\mathrm{import}} \mapsfrom s_{\mathrm{import}}},\overline{s_{\mathrm{export}} \mapsto w_{\mathrm{export}}},\sigrets,\sigcloss) \tand \\
      &\qquad\text{For all } W' \future W \ldotp \\
      &\qquad\quad\text{If } \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}\\
      &\qquad\quad\text{and } \msdata' = \msdata{}[\overline{a_{\mathrm{import}} \mapsto w_{\mathrm{import}}}] \\
      &\qquad\quad\text{then } \npair{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata', \mscode\uplus\msdata')} \in \lrheap(\pwheap)(W') \tand\\
      &\qquad\quad\overline{\npair{(w_{\mathrm{export}},w_{\mathrm{export}})}} \in \lrv(\purePart{W'})
  \end{aligned}
    \right\}\\
  &\cup \left\{
    \begin{multlined}
     \npair{(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}),(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})} \;\mid \;\\
     \npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W) \tand\\
     \{(\_ \mapsto c_{\mathrm{main},c}),(\_ \mapsto c_{\mathrm{main},d})\} \subseteq \overline{w_{\mathrm{export}}}
       \end{multlined}
    \right\} 
\end{align*}

@@

  Now take $W' \future (W_1\uplus W_2)$ and assume that $\overline{\npair[n']{(w_{\mathrm{import},3},w_{\mathrm{import},3})}} \in \lrv(\purePart{W'})$ for all $n' < n$.
  Take $\overline{\var{import}_3} = \overline{a_{\mathrm{import},3} \mapsfrom s_{\mathrm{import},3}}$.
  Take $\msdata[3]' = \msdata[3]{}[\overline{a_{\mathrm{import},3} \mapsto w_{\mathrm{import}}}]$
  Then it remains to show that
  \begin{equation*}
    \npair{(\sigrets[3]\uplus\sigcloss[3],\mscode[3]\uplus \msdata[3]', \mscode[3]\uplus\msdata[3]')} \in \lrheap(\pwheap[(W_1\uplus W_2)])(W')
  \end{equation*}
  and
  \begin{equation*}
    \overline{\npair{(c_{\mathrm{export},3},c_{\mathrm{export},3})}} \in \lrv(\purePart{W'})
  \end{equation*}
  We do this by complete induction on $n$, so that we can assume that $\overline{\npair[n']{(c_{\mathrm{export},3},c_{\mathrm{export},3})}} \in \lrv(\purePart{W'})$ for all $n' < n$.

@@

  Then, it follows from our assumptions ($\npair{(\var{comp}_1,\var{comp}_1)} \in \lrcomp(W_1)$ and $\npair{(\var{comp}_2,\var{comp}_2)} \in \lrcomp(W_2)$), and using Lemma~\ref{lem:uplus-future} that
  \begin{align*}
    \npair{(\sigrets[1]\uplus\sigcloss[1],\mscode[1]\uplus \msdata[1]', \mscode[1]\uplus\msdata[1]')} &\in \lrheap(\pwheap[W_1])(W')\\
    \npair{(\sigrets[2]\uplus\sigcloss[2],\mscode[2]\uplus \msdata[2]', \mscode[2]\uplus\msdata[2]')} &\in \lrheap(\pwheap[W_2])(W')
  \end{align*}
  It follows by Lemma~\ref{lem:combined-memory-disjoint-world} that 
  \begin{equation*}
    \npair{(\sigrets[3]\uplus\sigcloss[3],\mscode[3]\uplus \msdata[3]', \mscode[3]\uplus\msdata[3]')} \in \lrheap(\pwheap[(W_1\uplus W_2)])(W')
  \end{equation*}

@@

  It now remains to prove that $\npair{(\var{comp},\var{comp})} \in \lrcomp{W}$.
  Take $W' \future W$ and assume that
  \begin{equation*}
    \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}\\
  \end{equation*}
  and
  \begin{equation*}
    \msdata' = \msdata{}[\overline{a_{\mathrm{import}} \mapsto w_{\mathrm{import}}}] \\
  \end{equation*}
  We need to show that
  \begin{itemize}
  \item
    \begin{equation*}
      \npair{(\sigrets\uplus\sigcloss,\mspad\uplus\mscode\uplus \msdata', \mspad\uplus\mscode\uplus\msdata')} \in \lrheap(\pwheap)(W')
    \end{equation*}
   Take $R_\ms : \dom(\activeReg{\pwheap}) \fun \MemSeg \times \MemSeg$ such that
    \begin{itemize}
    \item $R_\ms(r_\addr) = (\msdata|_{\{a\}}, \msdata|_{\{a\}})$.
    \item $R_\ms(r_\var{code}) = (\mspad\uplus\mscode,\mspad\uplus\mscode)$
    \end{itemize}
    Take $R_W' : \dom(\activeReg{\pwheap}) \fun \World$ such that
    \begin{itemize}
    \item $R_W'(r_\addr) = \purePart{W}[\var{heap}.r_{\addr'}\mapsto \stdreg{\{\aaddr\},\gc}{\spatialo}]_{\addr' \in A_\var{own}(\addr)}$ 
    \item $R_W'(r_\var{code}) = \purePart{W}$
    \end{itemize}
    Since then $W = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W'(r)$, we can use Lemma~\ref{lem:oplus-future-distr} to construct an $R_W$ with  $W' = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W(r)$ and $R_W(r) \future R_W'(r)$ for all $r$.
    Finally, take $R_\var{seal} : \dom(\activeReg{\pwheap}) \fun \powerset{\Seal}$ to satisfy
    \begin{itemize}
    \item $R_\var{seal}(r_\addr) = \emptyset$
    \item $R_\var{seal}(r_\var{code}) = \sigrets\uplus \sigcloss$.
    \end{itemize}

    We then need to prove that 
    \begin{itemize}
    \item $\npair{(\msdata'|_{\{\addr\}},\msdata'|_{\{\addr\}})} \in \stdreg{\{\aaddr\},\gc}{\lin}.H~ \xi^{-1}(R_W(r_\addr))$:
      By definition, it suffices to prove that for all $n' < n$,
      $\npair[n']{(\msdata'(\addr),\msdata'(\addr))} \in \lrv(R_W(r_\addr))$.

      If $(a \mapsfrom \_) \in \overline{\var{import}}$, then we know that $\msdata'(a)$ is the corresponding $w_{\mathrm{import}}$ and the result is fine by the assumption that
      \begin{equation*}
        \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}\\
      \end{equation*}
      together with \ref{lem:monotonicity} and the fact that $R_W(\addr) \future \purePart{W'}$ (by Lemma~\ref{lem:auth-partial-betterthannothing}).

@@

      By Lemma~\ref{lem:ftlr-comp-value}, it then suffices to prove that
      \begin{itemize}
      \item $\npair{A_{\mathrm{non-linear}}} \in \readCond{\normal,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\npair{A_{\mathrm{non-linear}}} \in \writeCond{\normal,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\npair{A_{\mathrm{own}}(\addr)} \in \readCond{\linear,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\npair{A_{\mathrm{own}}(\addr)} \in \writeCond{\linear,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\pwheap[R_W(\addr)](r_{\mathrm{code}}) = \codereg{\sigrets,\sigcloss,\mscode,\gc}$: follows from the choice of $W$ and $R_W'(\addr)$ and the fact that $R_W(a) \future R_W'(a)$
      \item $\dom(\mscode) \mathrel{\#} \ta$ or $\dom(\mscode) \subseteq \ta$: by assumption.
      \end{itemize}
    \item $\npair{(\mspad\uplus\mscode,\mspad\uplus\mscode)} \in  \codereg[\mathrm{code},\square]{\sigrets,\sigcloss,\mscode,\gc}.H~ \xi^{-1}(\purePart{W'})$:
      We take $\trust = \trusted$ if $[\baddr-1,\eaddr+1] \subseteq \ta$ and $\trust =\untrusted$ otherwise.
      By definition, we need to prove that:

      \begin{itemize}
      \item $\dom(\code) = [\baddr,\eaddr]$: by assumption.
      \item $([\baddr-1,\eaddr+1] \wedge \trust = \trusted) \vee ([\baddr-1,\eaddr+1]\mathrel{\#} \ta \wedge \sigrets = \emptyset \wedge \trust =\untrusted)$: by assumption and choice of $\trust$.
      \item $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code$: by assumption.
      \item $\mspad = [\baddr-1 \mapsto 0] \uplus [\eaddr + 1 \mapsto 0]$:
        by assumption
      \item $\forall a \in \dom(\code), n' < n \ldotp \npair[n']{(\code(a),\code(a))} \in \lrvg{\trust}(\purePart{}(\xi(\xi^{-1}(\purePart{W'}))))$:
        Note first that $\purePart{}(\xi(\xi^{-1}(\purePart{W'}))) =\purePart{W'}$.

@@

  From $\npair{(\var{comp},\var{comp})} \in \lrcomp(W)$, we know that
  $\{(\_ \mapsto c_{\mathrm{main},c}), (\_ \mapsto c_{\mathrm{main},d})\}\subseteq \overline{\var{export}}$ and 
  $\npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W)$ with $\var{comp}_0 = (\mscode, \msdata, \overline{a_{\mathrm{import}}\mapsfrom s_{\mathrm{import}}}, \overline{s_{\mathrm{export}}\mapsto w_{\mathrm{export}}}, \sigrets, \sigcloss,A_\linear)$.
  From this, it follows that for all  $W' \future W$, if
  \begin{equation*}
    \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}
  \end{equation*}
  and $\msdata' = \msdata{}[\overline{a_{\mathrm{import}} \mapsto w_{\mathrm{import}}}]$
  then
  \begin{equation*}
    \npair{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata', \mscode\uplus\msdata')} \in \lrheap(\pwheap)(W')
  \end{equation*}
  and
  \begin{equation*}
    \overline{\npair{(w_{\mathrm{export}},w_{\mathrm{export}})}} \in \lrv(\purePart{W'})
  \end{equation*}
  Since $\overline{w_{\mathrm{import}}} = \emptyset$, the former holds vacuously, $\msdata' = \msdata$ and the latter two results follow for every $W' \future W$.

@@

  \item $\memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W_M}$:
    Since $W_M \future W$, we have seen above that 
    \begin{equation*}
      \npair{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata, \mscode\uplus\msdata)} \in \lrheap(\pwheap[W_M])(W_M)
    \end{equation*}
    and hence by Lemma~\ref{lem:downwards-closed}:
    \begin{equation*}
      \npair[n']{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata, \mscode\uplus\msdata)} \in \lrheap(\pwheap[W_M])(W_M)
    \end{equation*}
    It suffices to prove that also
    \begin{itemize}
    \item $\memSatStack[n']{\emptyset,\emptyset}{\purePart{W_M}}$
    \item $\memSatFStack[n']{\ms_\stk,\ms_\stk}{\purePart{W_M}}$
    \end{itemize}
    The former follows vacuously.
    The latter follows by taking $R_\ms(r_a) = (\ms_\stk|_{\{a\}},\ms_\stk|_{\{a\}})$, $R_W(r_a) = \purePart{W_M}$ for $a \in [\baddr_\stk,\eaddr_\stk]$ by Lemma~\ref{lem:purePart-duplicable} and~\ref{lem:purePart-idempotent} if we can show that:
    \begin{equation*}
      \npair[n']{(\ms_\stk|_{\{a\}},\ms_\stk|_{\{a\}})} \in \stdreg{\{a\},\gc}{\spatialo}.H~ \xi^{-1}(\purePart{W_M})
    \end{equation*}
    By definition, it suffices to show that for all $n'' < n'$, we have that:
    \begin{equation*}
      \npair[n'']{(\ms_\stk(a),\ms_\stk(a)) \in \lrv(\purePart{W_M})}
    \end{equation*}
    But $\ms_\stk(a) = 0$, so this follows easily by definition.

@@

\begin{lemma}[Compatibility lemma for context plugging]
  \label{lem:compat-context-plug}
  If $\npair{\stpair{C}{C}}\in\lrcomp(W_1)$ and $\npair{\stpair{P}{P}} \in \lrcomp(W_2)$, then
  $\npair{(\plug{C_S}{P_S},\plug{C_T}{P_T})} \in \lrec(W_1 \uplus W_2)$.
\end{lemma}
\begin{proof}
  By definition, we have that $C_S \bowtie P_S \rightsquigarrow C_S[P_S]$ and $C_T \bowtie P_T \rightsquigarrow C_T[P_T]$.

@@

    First, we show that also $\plug{\context}{\var{comp}_1} \trg{\term}$.
    Take $n$ the amount of steps in the termination of $\src{\plug{\context}{\var{comp}_1} \sterm{\gc_1}}$.
    It follows from Lemma~\ref{lem:ftlr-comps} that $\npair{(\var{comp}_1,\var{comp}_1)} \in \lrcomp[\preceq,\gc_1](W_1)$ for some $W_1$ with $\dom(\pwfree) = \dom(\pwpriv) = \emptyset$.
    It also follows from the same Lemma~\ref{lem:ftlr-comps} that $\npair{(\context,\context)} \in \lrcomp[\preceq,\gc_1](W_1')$ for some $W_1'$ that we can choose such that $W_1 \uplus W_1'$ is defined.
    Lemma~\ref{lem:compat-context-plug} then tells us that $\npair{(\plug{\context}{\var{comp}_1}, \plug{\context}{\var{comp}_1})} \in \lrec[\preceq,\gc_1](W_1\uplus W_1')$
    Together with $\src{\plug{\context}{\var{comp}_1} \sterm[n]{\gc_1}}$, Lemma~\ref{lem:adequacy} then tells us that $\plug{\context}{\var{comp}_1} \trg{\term}$.

@@

    It now remains to show that also $\src{\plug{\context}{\var{comp}_2} \sterm{\gc_2}}$.
    Take $n'$ the amount of steps in the termination of $\plug{\context}{\var{comp}_2} \trg{\term}$.
    It follows from Lemma~\ref{lem:ftlr-comps} that $\npair[n']{(\var{comp}_2,\var{comp}_2)} \in \lrcomp[\succeq,\gc_2](W_2)$ for some $W_2$ with $\dom(\pwfree) = \dom(\pwpriv) = \emptyset$.
    It also follows from the same Lemma~\ref{lem:ftlr-comps} that $\npair[n']{(\context,\context)} \in \lrcomp[\succeq,\gc_2](W_2')$ for some $W_2'$ that we can choose such that $W_2 \uplus W_2'$ is defined.
    Lemma~\ref{lem:compat-context-plug} then tells us that $\npair[n']{(\plug{\context}{\var{comp}_2}, \plug{\context}{\var{comp}_2})} \in \lrec[\succeq,\gc_2](W_2\uplus W_2')$
    Together with $\plug{\context}{\var{comp}_2} \trg{\term[n']}$, Lemma~\ref{lem:adequacy} then tells us that $\src{\plug{\context}{\var{comp}_2} \sterm{\gc_2}}$, concluding this direction of the proof.

>>>>

\begin{align*}
  \lrcomp(W) &=
  \left\{\begin{aligned}
     &\npair{\var{comp},\var{comp}} \;\mid \;\\
      &\qquad\var{comp} = (\mscode,\msdata,\overline{a_{\mathrm{import}} \mapsfrom s_{\mathrm{import}}},\overline{s_{\mathrm{export}} \mapsto w_{\mathrm{export}}},\sigrets,\sigcloss) \tand \\
      &\qquad\text{For all } W' \future W \ldotp \\
      &\qquad\quad\text{If } \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}\\
      &\qquad\quad\text{and } \msdata' = \msdata{}[\overline{a_{\mathrm{import}} \mapsto w_{\mathrm{import}}}] \\
      &\qquad\quad\text{then } \npair[n']{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata', \mscode\uplus\msdata')} \in \lrheap(\pwheap)(W') \text{ for all $n' < n$} \tand\\
      &\qquad\quad\overline{\npair{(w_{\mathrm{export}},w_{\mathrm{export}})}} \in \lrv(\purePart{W'})
  \end{aligned}
    \right\}\\
  &\cup \left\{
    \begin{multlined}
     \npair{(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}),(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})} \;\mid \;\\
     \npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W) \tand\\
     \{(\_ \mapsto c_{\mathrm{main},c}),(\_ \mapsto c_{\mathrm{main},d})\} \subseteq \overline{w_{\mathrm{export}}}
       \end{multlined}
    \right\} 
\end{align*}

@@

  Now take $W' \future (W_1\uplus W_2)$ and assume that $\overline{\npair[n']{(w_{\mathrm{import},3},w_{\mathrm{import},3})}} \in \lrv(\purePart{W'})$ for all $n' < n$.
  Take $\overline{\var{import}_3} = \overline{a_{\mathrm{import},3} \mapsfrom s_{\mathrm{import},3}}$.
  Take $\msdata[3]' = \msdata[3]{}[\overline{a_{\mathrm{import},3} \mapsto w_{\mathrm{import}}}]$
  Then it remains to show that
  \begin{equation*}
    \npair[n']{(\sigrets[3]\uplus\sigcloss[3],\mscode[3]\uplus \msdata[3]', \mscode[3]\uplus\msdata[3]')} \in \lrheap(\pwheap[(W_1\uplus W_2)])(W')
  \end{equation*}
  for all $n' < n$ and
  \begin{equation*}
    \overline{\npair{(c_{\mathrm{export},3},c_{\mathrm{export},3})}} \in \lrv(\purePart{W'})
  \end{equation*}
  We do this by complete induction on $n$, so that we can assume that $\overline{\npair[n']{(c_{\mathrm{export},3},c_{\mathrm{export},3})}} \in \lrv(\purePart{W'})$ for all $n' < n$.

@@

  Then, it follows from our assumptions ($\npair{(\var{comp}_1,\var{comp}_1)} \in \lrcomp(W_1)$ and $\npair{(\var{comp}_2,\var{comp}_2)} \in \lrcomp(W_2)$), and using Lemma~\ref{lem:uplus-future} that
  \begin{align*}
    \npair[n']{(\sigrets[1]\uplus\sigcloss[1],\mscode[1]\uplus \msdata[1]', \mscode[1]\uplus\msdata[1]')} &\in \lrheap(\pwheap[W_1])(W')\\
    \npair[n']{(\sigrets[2]\uplus\sigcloss[2],\mscode[2]\uplus \msdata[2]', \mscode[2]\uplus\msdata[2]')} &\in \lrheap(\pwheap[W_2])(W')
  \end{align*}
  for all $n' < n$.
  It follows by Lemma~\ref{lem:combined-memory-disjoint-world} that 
  \begin{equation*}
    \npair[n']{(\sigrets[3]\uplus\sigcloss[3],\mscode[3]\uplus \msdata[3]', \mscode[3]\uplus\msdata[3]')} \in \lrheap(\pwheap[(W_1\uplus W_2)])(W')
  \end{equation*}
  for all $n' < n$.

@@

  It now remains to prove that $\npair{(\var{comp},\var{comp})} \in \lrcomp{W}$.
  Take $W' \future W$ and assume that
  \begin{equation*}
    \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}\\
  \end{equation*}
  and
  \begin{equation*}
    \msdata' = \msdata{}[\overline{a_{\mathrm{import}} \mapsto w_{\mathrm{import}}}] \\
  \end{equation*}
  We need to show that
  \begin{itemize}
  \item
    \begin{equation*}
      \npair[n']{(\sigrets\uplus\sigcloss,\mspad\uplus\mscode\uplus \msdata', \mspad\uplus\mscode\uplus\msdata')} \in \lrheap(\pwheap)(W')
    \end{equation*}
    for all $n' < n$.

   Take $R_\ms : \dom(\activeReg{\pwheap}) \fun \MemSeg \times \MemSeg$ such that
    \begin{itemize}
    \item $R_\ms(r_\addr) = (\msdata|_{\{a\}}, \msdata|_{\{a\}})$.
    \item $R_\ms(r_\var{code}) = (\mspad\uplus\mscode,\mspad\uplus\mscode)$
    \end{itemize}
    Take $R_W' : \dom(\activeReg{\pwheap}) \fun \World$ such that
    \begin{itemize}
    \item $R_W'(r_\addr) = \purePart{W}[\var{heap}.r_{\addr'}\mapsto \stdreg{\{\aaddr\},\gc}{\spatialo}]_{\addr' \in A_\var{own}(\addr)}$ 
    \item $R_W'(r_\var{code}) = \purePart{W}$
    \end{itemize}
    Since then $W = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W'(r)$, we can use Lemma~\ref{lem:oplus-future-distr} to construct an $R_W$ with  $W' = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W(r)$ and $R_W(r) \future R_W'(r)$ for all $r$.
    Finally, take $R_\var{seal} : \dom(\activeReg{\pwheap}) \fun \powerset{\Seal}$ to satisfy
    \begin{itemize}
    \item $R_\var{seal}(r_\addr) = \emptyset$
    \item $R_\var{seal}(r_\var{code}) = \sigrets\uplus \sigcloss$.
    \end{itemize}

    We then need to prove that 
    \begin{itemize}
    \item $\npair[n']{(\msdata'|_{\{\addr\}},\msdata'|_{\{\addr\}})} \in \stdreg{\{\aaddr\},\gc}{\lin}.H~ \xi^{-1}(R_W(r_\addr))$ for all $n' < n$:
      Take $n' < n$.
      By definition, it suffices to prove that,
      $\npair[n']{(\msdata'(\addr),\msdata'(\addr))} \in \lrv(R_W(r_\addr))$.

      If $(a \mapsfrom \_) \in \overline{\var{import}}$, then we know that $\msdata'(a)$ is the corresponding $w_{\mathrm{import}}$ and the result is fine by the assumption that
      \begin{equation*}
        \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'})
      \end{equation*}
      together with \ref{lem:monotonicity} and the fact that $R_W(\addr) \future \purePart{W'}$ (by Lemma~\ref{lem:auth-partial-betterthannothing}).

@@

      By Lemma~\ref{lem:ftlr-comp-value}, it then suffices to prove that
      \begin{itemize}
      \item $\npair[n']{A_{\mathrm{non-linear}}} \in \readCond{\normal,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\npair[n']{A_{\mathrm{non-linear}}} \in \writeCond{\normal,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\npair[n']{A_{\mathrm{own}}(\addr)} \in \readCond{\linear,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\npair[n']{A_{\mathrm{own}}(\addr)} \in \writeCond{\linear,R_W(\addr)}$: follows by Lemma~\ref{lem:monotonicity} using the fact that $R_W(a) \future R_W'(a)$ and by definition, using the choice of $W$, $R_W'(\addr)$ 
      \item $\pwheap[R_W(\addr)](r_{\mathrm{code}}) = \codereg{\sigrets,\sigcloss,\mscode,\gc}$: follows from the choice of $W$ and $R_W'(\addr)$ and the fact that $R_W(a) \future R_W'(a)$
      \item $\dom(\mscode) \mathrel{\#} \ta$ or $\dom(\mscode) \subseteq \ta$: by assumption.
      \end{itemize}
    \item $\npair[n']{(\mspad\uplus\mscode,\mspad\uplus\mscode)} \in  \codereg[\mathrm{code},\square]{\sigrets,\sigcloss,\mscode,\gc}.H~ \xi^{-1}(\purePart{W'})$ for all $n' < n$:
      Take $n' < n$.
      We take $\trust = \trusted$ if $[\baddr-1,\eaddr+1] \subseteq \ta$ and $\trust =\untrusted$ otherwise.
      By definition, we need to prove that:

      \begin{itemize}
      \item $\dom(\code) = [\baddr,\eaddr]$: by assumption.
      \item $([\baddr-1,\eaddr+1] \wedge \trust = \trusted) \vee ([\baddr-1,\eaddr+1]\mathrel{\#} \ta \wedge \sigrets = \emptyset \wedge \trust =\untrusted)$: by assumption and choice of $\trust$.
      \item $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code$: by assumption.
      \item $\mspad = [\baddr-1 \mapsto 0] \uplus [\eaddr + 1 \mapsto 0]$:
        by assumption
      \item $\forall a \in \dom(\code) \ldotp \npair[n']{(\code(a),\code(a))} \in \lrvg{\trust}(\purePart{}(\xi(\xi^{-1}(\purePart{W'}))))$:
        Note first that $\purePart{}(\xi(\xi^{-1}(\purePart{W'}))) =\purePart{W'}$.

@@

  From $\npair{(\var{comp},\var{comp})} \in \lrcomp(W)$, we know that
  $\{(\_ \mapsto c_{\mathrm{main},c}), (\_ \mapsto c_{\mathrm{main},d})\}\subseteq \overline{\var{export}}$ and 
  $\npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W)$ with $\var{comp}_0 = (\mscode, \msdata, \overline{a_{\mathrm{import}}\mapsfrom s_{\mathrm{import}}}, \overline{s_{\mathrm{export}}\mapsto w_{\mathrm{export}}}, \sigrets, \sigcloss,A_\linear)$.
  From this, it follows that for all  $W' \future W$, if
  \begin{equation*}
    \overline{\npair[n']{(w_{\mathrm{import}},w_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}
  \end{equation*}
  and $\msdata' = \msdata{}[\overline{a_{\mathrm{import}} \mapsto w_{\mathrm{import}}}]$
  then
  \begin{equation*}
    \npair[n']{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata', \mscode\uplus\msdata')} \in \lrheap(\pwheap)(W')
  \end{equation*}
  for all $n' < n$ and
  \begin{equation*}
    \overline{\npair{(w_{\mathrm{export}},w_{\mathrm{export}})}} \in \lrv(\purePart{W'})
  \end{equation*}
  Since $\overline{w_{\mathrm{import}}} = \emptyset$, the former holds vacuously, $\msdata' = \msdata$ and the latter two results follow for every $W' \future W$.

@@

  \item $\memSat[n']{\ms_S,\ms_\stk,\stk,\ms_T}{W_M}$:
    Since $W_M \future W$, we have seen above that 
    \begin{equation*}
      \npair[n']{(\sigrets\uplus\sigcloss,\mscode\uplus \msdata, \mscode\uplus\msdata)} \in \lrheap(\pwheap[W_M])(W_M)
    \end{equation*}
    It suffices to prove that also
    \begin{itemize}
    \item $\memSatStack[n']{\emptyset,\emptyset}{\purePart{W_M}}$
    \item $\memSatFStack[n']{\ms_\stk,\ms_\stk}{\purePart{W_M}}$
    \end{itemize}
    The former follows vacuously.
    The latter follows by taking $R_\ms(r_a) = (\ms_\stk|_{\{a\}},\ms_\stk|_{\{a\}})$, $R_W(r_a) = \purePart{W_M}$ for $a \in [\baddr_\stk,\eaddr_\stk]$ by Lemma~\ref{lem:purePart-duplicable} and~\ref{lem:purePart-idempotent} if we can show that:
    \begin{equation*}
      \npair[n']{(\ms_\stk|_{\{a\}},\ms_\stk|_{\{a\}})} \in \stdreg{\{a\},\gc}{\spatialo}.H~ \xi^{-1}(\purePart{W_M})
    \end{equation*}
    By definition, it suffices to show that for all $n'' < n'$, we have that:
    \begin{equation*}
      \npair[n'']{(\ms_\stk(a),\ms_\stk(a)) \in \lrv(\purePart{W_M})}
    \end{equation*}
    But $\ms_\stk(a) = 0$, so this follows easily by definition.

@@

\begin{lemma}[Compatibility lemma for context plugging]
  \label{lem:compat-context-plug}
  If $\npair{\stpair{C}{C}}\in\lrcomp(W_1)$ and $\npair{\stpair{P}{P}} \in \lrcomp(W_2)$, then
  $\npair[n']{(\plug{C_S}{P_S},\plug{C_T}{P_T})} \in \lrec(W_1 \uplus W_2)$, for all $n' < n$.
\end{lemma}
\begin{proof}
  By definition, we have that $C_S \bowtie P_S \rightsquigarrow C_S[P_S]$ and $C_T \bowtie P_T \rightsquigarrow C_T[P_T]$.

@@

    First, we show that also $\plug{\context}{\var{comp}_1} \trg{\term}$.
    Take $n$ the amount of steps in the termination of $\src{\plug{\context}{\var{comp}_1} \sterm{\gc_1}}$.
    It follows from Lemma~\ref{lem:ftlr-comps} that $\npair[n+1]{(\var{comp}_1,\var{comp}_1)} \in \lrcomp[\preceq,\gc_1](W_1)$ for some $W_1$ with $\dom(\pwfree) = \dom(\pwpriv) = \emptyset$.
    It also follows from the same Lemma~\ref{lem:ftlr-comps} that $\npair[n+1]{(\context,\context)} \in \lrcomp[\preceq,\gc_1](W_1')$ for some $W_1'$ that we can choose such that $W_1 \uplus W_1'$ is defined.
    Lemma~\ref{lem:compat-context-plug} then tells us that $\npair{(\plug{\context}{\var{comp}_1}, \plug{\context}{\var{comp}_1})} \in \lrec[\preceq,\gc_1](W_1\uplus W_1')$
    Together with $\src{\plug{\context}{\var{comp}_1} \sterm[n]{\gc_1}}$, Lemma~\ref{lem:adequacy} then tells us that $\plug{\context}{\var{comp}_1} \trg{\term}$.

@@

    It now remains to show that also $\src{\plug{\context}{\var{comp}_2} \sterm{\gc_2}}$.
    Take $n'$ the amount of steps in the termination of $\plug{\context}{\var{comp}_2} \trg{\term}$.
    It follows from Lemma~\ref{lem:ftlr-comps} that $\npair[n'+1]{(\var{comp}_2,\var{comp}_2)} \in \lrcomp[\succeq,\gc_2](W_2)$ for some $W_2$ with $\dom(\pwfree) = \dom(\pwpriv) = \emptyset$.
    It also follows from the same Lemma~\ref{lem:ftlr-comps} that $\npair[n'+1]{(\context,\context)} \in \lrcomp[\succeq,\gc_2](W_2')$ for some $W_2'$ that we can choose such that $W_2 \uplus W_2'$ is defined.
    Lemma~\ref{lem:compat-context-plug} then tells us that $\npair[n']{(\plug{\context}{\var{comp}_2}, \plug{\context}{\var{comp}_2})} \in \lrec[\succeq,\gc_2](W_2\uplus W_2')$
    Together with $\plug{\context}{\var{comp}_2} \trg{\term[n']}$, Lemma~\ref{lem:adequacy} then tells us that $\src{\plug{\context}{\var{comp}_2} \sterm{\gc_2}}$, concluding this direction of the proof.
